---
title: "Amazon Business Report"
output: html_document
date: "2023-11-26"
---


**This report focuses on Amazon's business in India, encompassing sales across various clothing categories shipped throughout the country from March to June. Our exploration will include gaining insights into monthly sales, identifying the top 10 cities with the highest sales-to-order ratio, examining the B2B business aspect, and more. Let's commence the exploration . . .**

```{r include = FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(stringr)
library(scales)

sales_data <- read.csv("C:\\Users\\HP\\OneDrive\\Google Data Analytics\\Project\\Amazon Sales\\data\\Amazon Sale Report.csv")
palettes <- list(
    MediumVioletRed = "#C71585",
    Tomato = "#FF6347",
    Gold = "#FFD700",
    Yellow = "#FFFF00",
    RebeccaPurple = "#663399",
    Indigo = "#4B0082",
    LimeGreen = "#32CD32",
    MediumSeaGreen = "#3CB371",
    DarkGreen = "#006400",
    SpringGreen = "#00FF7F",
    GreenYellow = "#ADFF2F",
    Lime = "#00FF00",
    Teal = "#008080",
    CadetBlue = "#5F9EA0",
    MidnightBlue = "#191970",
    White = "#FFFFFF",
    DarkOrange = "#FF8C00",
    Coral = "#FF7F50",
    OrangeRed = "#FF4500",
    LightSalmon = "#FFA07A"
)

sales_data <- na.omit(sales_data)

clean_data <- unique(sales_data) %>%
  mutate(
    Date = mdy(Date),
    Status = Status,
    Fulfilment = Fulfilment, # Amazon, Merchant
    Sales_Channel = Sales.Channel, # Aamazon.in
    Ship_Service_Level = ship.service.level, # Expedited (Fast), Standard
    Category = Category, # Product Category
    Size = Size,
    Courier_Status = Courier.Status, # The count of "" category is 5133, make sure. 
    Amount = as.double(Amount),
    Ship_City = str_to_title(ship.city),
    Ship_State = str_to_title(ship.state),
    Ship_Country = ship.country,
    B2B = ifelse(B2B == "True", 1, 0)
  ) %>%
  select(Date, Status, Fulfilment, Sales_Channel, Ship_Service_Level, 
         Category, Size, Courier_Status, Amount, Ship_City, Ship_State,
         Ship_Country, B2B)
```

```{r include = FALSE}
kpi <- clean_data %>%
  summarise(Revenue = sprintf("%0.1fM", sum(Amount) / 1e6),
            Unshipped_Count = length(Courier_Status[Courier_Status == "Unshipped"]),
            B2B_Sales = sum(B2B),
            B2B_Ratio = paste(round((sum(B2B) / n()) * 100, 2), "%", sep = "")
            )
kpi_measures <- data.frame(Labels = c("Revenue", "Unshipped Count", "B2B Sales", "B2B Ratio"),
                           Shapes = c(1),
                           Values = c(kpi$Revenue, kpi$Unshipped_Count, kpi$B2B_Sales, kpi$B2B_Ratio)
                           )
```

### KPI (Key Performance Indiator)

This indicator offers an overview of Amazon's business in India. We will delve into the overall revenue generated over time, the B2B business aspect, and the quantity of un-shipped items.
``` {r kpi_measures, echo = FALSE, warning = FALSE}
ggplot(data = kpi_measures, aes(x = Shapes, y = Labels)) + 
  geom_bar(stat = "identity", fill = palettes$White) + 
  geom_text(aes(label = Values), hjust = 1, size = 12, 
            fontface = "bold", color = palettes$Gold) + 
  scale_x_continuous(breaks = NULL) + 
  theme_minimal() + 
  theme(
    axis.text.y = element_text(colour = palettes$RebeccaPurple),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    axis.text.y.left = element_text(size = 15)
  )
```

### 1.    Sales over the Period of Months

This provides a summary of Amazon.in sales from March to June. It is noticeable that sales declined during this period, possibly influenced by festivals in April and May. Additionally, the onset of rain in June is a common factor contributing to reduced sales. March, however, stands out as an exceptional month, where sales were minimal, potentially due to ongoing exams in India during that time. 
```{r include = FALSE}
sales_over_months <- clean_data %>%
  group_by(Months = format(Date, "%B")) %>%
  summarise(Revenue = sum(Amount))

sales_over_months <- sales_over_months[order(-sales_over_months$Revenue), ]
sales_over_months$Months <- factor(sales_over_months$Months, levels = sales_over_months$Months)
```

```{r sales_over_months, echo = FALSE, warning = FALSE}
ggplot(data = sales_over_months, aes(x = Months, y = Revenue, fill = Months)) + 
  geom_bar(stat = "identity") + 
  scale_y_continuous(labels = label_number_si(scale = 1e-6, suffix = "M", accuracy = 0.01)) +
  scale_fill_manual(values = c("March" = palettes$Tomato, "April" = palettes$LimeGreen,
                               "May" = palettes$Gold, "June" = palettes$DarkOrange)) + 
  theme_minimal() + 
  theme(
    panel.grid = element_blank(),
    axis.title = element_blank(),
    axis.text = element_text(color = palettes$RebeccaPurple)
  )
```

### 2.    Affection of Un-shipped Item

The information presented in this pie chart sheds light on the impact of delayed product shipping, which adversely affects company sales. Approximately 84% of sales are lost due to delays in the supply, with some items still in the midst of the delivery process. 
```{r include = FALSE}
status_unshipped <- clean_data %>%
  group_by(Courier_Status, Status) %>%
  summarise(Count = n()) %>%
  filter(Courier_Status == "Unshipped")
```

```{r status_unshipped, echo=FALSE, warning=FALSE}
ggplot(data = status_unshipped, aes(x = "", y = -Count, fill = status_unshipped$Status)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label = Count), 
                  position = position_stack(vjust = 0.5)) + 
  coord_polar(theta = "y", start = 0, direction = -1) + 
  scale_y_continuous(breaks = NULL) + 
  scale_fill_manual(values = c("Cancelled" = palettes$OrangeRed, "Pending" = palettes$Coral,
                               "Pending - Waiting for Pick Up" = palettes$LightSalmon)) + 
  theme_minimal() + 
  theme(
    panel.grid = element_blank(),
    axis.title = element_blank()
  )
```

### 3.    Top 10 Cities Placed Order


The graph displays the names of the top 10 cities in India that received substantial numbers of orders and generated significant revenue. Notably, Bengaluru and Hyderabad stand out with the highest sales, receiving approximately 11.3K and 8.6K orders, respectively.

```{r include=FALSE}
top_cities_placed_ordered <- clean_data %>%
  group_by(Ship_City) %>%
  summarise(Orders_Count = n(), 
            Revenue = sum(Amount)) %>%
  arrange(desc(Revenue)) %>%
  head(10)

top_cities_placed_ordered <- top_cities_placed_ordered[order(-top_cities_placed_ordered$Revenue), ]
top_cities_placed_ordered$Ship_City <- factor(top_cities_placed_ordered$Ship_City, 
                                              levels = rev(top_cities_placed_ordered$Ship_City))
```

```{r top_cities_placed_order, echo=FALSE, warning=FALSE}
ggplot(data = top_cities_placed_ordered, aes(y = Ship_City)) + 
  geom_bar(aes(x = Revenue, fill = "Revenue"), stat = "identity") + 
  geom_text(aes(x = Revenue, label = sprintf("%0.1fM", (Revenue / 1e6))), 
            hjust = -0.2) + 
  geom_bar(aes(x = Orders_Count*100, fill = "Orders_Count"), stat = "identity") + 
  geom_text(aes(x = Orders_Count, label = sprintf("%0.1fK", (Orders_Count / 1000))), 
            vjust = 0.5, hjust = 0, size = 3, color = "#000456") + 
  scale_x_continuous(labels = label_number_si(scale = 1e-6, suffix = "M", accuracy = 0.01), 
                     "Revenue in Million",
                     sec.axis = sec_axis(~./100, name = "Orders Count in Thousand")) + 
  scale_fill_manual(values = c("Revenue" = palettes$LimeGreen, 
                               "Orders_Count" = palettes$Gold), name = "") + 
  theme_minimal() + 
  theme(
    panel.grid = element_blank(),
    axis.title = element_blank(),
    axis.text.x = element_blank(),
    legend.position = "bottom",
    aspect.ratio = 0.5
  )
```

### 4.    Maximum Sizes Ordered 

The bar graph provides insights into the demand for different clothing sizes, aiding in maintaining a consistent inventory. The top five sizes, namely Medium, Large, Extra-Large, Double Extra-Large, and Small, are depicted. However, among these, Medium, Large, and Extra-Large are the sizes that people most commonly prefer to order.
```{r include=FALSE}
sizes_ordered <- clean_data %>%
  group_by(Size) %>%
  summarise(Ordered_Count = n()) %>%
  arrange(desc(Ordered_Count)) %>%
  head(5)

sizes_ordered <- sizes_ordered[order(sizes_ordered$Ordered_Count), ]
sizes_ordered$Size <- factor(sizes_ordered$Size, level = rev(sizes_ordered$Size))
```

```{r sizes_ordered, echo=FALSE, warning=FALSE}
ggplot(data = sizes_ordered, aes(x = Size, y = Ordered_Count, fill = Ordered_Count)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label = Ordered_Count), vjust = -0.5) + 
  scale_y_continuous(breaks = NULL) + 
  scale_fill_gradient(low = palettes$DarkGreen, high = palettes$LimeGreen) + 
  theme_minimal() + 
  theme(
    panel.grid = element_blank(),
    axis.title = element_blank()
  ) + 
  guides(fill = FALSE)
```

### 5.    B2B Business

In this context, we will examine the performance of B2B sales, where Kurta and Set both are the categories of clothing sold nearly equal quantities as 319 and 327 respectively, but Set category has generated higher revenue, while Ethnic Dresses indicated lower demand.

```{r include=FALSE}
B2B_Sales <- clean_data %>%
  group_by(Category) %>%
  summarise(Order_Count = sum(B2B), Revenue = sum(Amount)) %>%
  arrange(desc(Order_Count)) %>%
  head(5)

B2B_Sales <- B2B_Sales[order(B2B_Sales$Order_Count), ]
B2B_Sales$Category <- factor(B2B_Sales$Category, levels = rev(B2B_Sales$Category))
```

```{r B2B_Sales, echo=FALSE, warning=FALSE}
ggplot(data = B2B_Sales, aes(x = Category)) + 
  geom_line(aes(y = Revenue, group = 1), linewidth = 1, color = palettes$Gold) + 
  geom_text(aes(y = Order_Count, label = Order_Count), vjust = -4) + 
  geom_bar(aes(y = Order_Count*10000, fill = Order_Count), stat = "identity") +
  scale_y_continuous("Revenue in Million",
                     labels = label_number_si(scale = 1e-6, suffix = "M", accuracy = 0.01),
                     sec.axis = sec_axis(~./10000, name = "Orders Count in Thousand")) +
  scale_fill_gradient(low = palettes$OrangeRed, high = palettes$Lime) + 
  theme_minimal() + 
  theme(
    panel.grid = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_text(colour = palettes$Indigo),
    axis.text = element_text(colour = palettes$RebeccaPurple)
  ) + 
  guides(fill = FALSE)
```

**In summary, upon examining these insights, it is recommended that Amazon formulate a business strategy. This strategy should include the creation of a special summer offer targeting the cities of Bengaluru, Hyderabad, and Mumbai, emphasizing popular clothing categories like Kurta and Set, making available in sizes Medium, Large, Extra-Large, Double Extra-Large, and Small. Additionally, vigilant monitoring of timely order deliveries to customer addresses is crucial.**